### 2018-12-04 README.Rmd
Generate Readme + add notes

The goal of fishcom is to ...

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```

>>>>

The goal of fishcom is to get all the informations concerning the ECOSTAB postdoc
project in one place including reproducible code, notes, eventually data and
manuscript.

## How to

My notes are available in the introductory vignette
[intro.html](https://github.com/alaindanet/fishcom/blob/master/vignettes/intro.html)
